---
title: "R Project 1 - Hello R"
author: "Muhammad Waleed Jamal"
date: "9/16/2020"
output: html_document
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1
```
A data frame with 1846 rows and 3 variables:

dataset: indicates which dataset the data are from

x: x-values

y: y-values
```
### Exercise 2
```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```


### Exercise 3


(Add code and narrative as needed. Note that the R chunks are labeled with `plot-star` and `cor-star` to provide spaces to place the code for plotting and calculating the correlation coefficient. To finish, remember to clean up the narrative by removing these instructions.)



```{r plot.stars, fig.height=4,fig.width=7}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data=dino_data,mapping=aes(x=x,y=y))+
  geom_point()

```

```{r cor-star}
dino_data %>%
  summarize(r=cor(x,y ))
```
### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)


```{r}
```




### Exercise 5
```{r plot}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```